---
title: "Project 1"
author: "Nate Mosley"
date: "March 20, 2017"
output: html_document
---

#This is the markdown document for Reproducible Research - Project 1.

##Loading and preprocessing the data
```{r}
tempfile <-"data.zip"
    if(!file.exists(tempfile)){
      fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"  
      download.file(fileUrl,tempfile)  
    }
if(!file.exists("activity.csv")){
      unzip(tempfile)
}
df<-read.csv("activity.csv", head=TRUE)
df$date<-as.Date(as.character(df$date),format="%Y-%m-%d")
echo=TRUE
```

##What is mean total number of steps taken per day?
#### This histogram shows the total number of steps taken per day  
```{r}
agg<-aggregate(df$steps, by=list(df$date),FUN=sum,na.rm=TRUE)
hist(agg$x, main = "Activity",xlab="Number of steps taken each day")
```

#### The mean total number of steps per day is:
```{r}
mean(agg$x, na.rm=TRUE)
```
#### The median total number of steps per day is:
```{r}
median(agg$x, na.rm=TRUE)
```

###What is the average daily activity pattern?
```{r}
agg2<-aggregate(df$steps, by=list(df$interval),FUN=mean, na.rm=TRUE)
colnames(agg2)<-c("interval","steps")
plot(agg2$interval, agg2$steps, type="l",col="red", main="Activity",xlab="Interval",ylab="Average Steps")
```

####The maximum number of steps taken per interval is:
```{r}
subset(agg2,agg2$steps==max(agg2$steps))
```

##Imputing missing values

####How many missing values are in the dataset?
```{r}
nrow(subset(df,is.na(df$steps)==TRUE))
```

####Fill the missing values with mean of the same interval
```{r}
getIntervalValue<-function(interval){
  IV<-NULL
  IV<-agg2[agg2$interval==interval,]$steps
  return(IV)
}


df.replaced.na<-df
for(i in 1:nrow(df.replaced.na)){
  if(is.na(df.replaced.na[i,]$steps)){
    df.replaced.na[i,]$steps<-getIntervalValue(df.replaced.na[i,]$interval)
  }
}

```
